---
title: "ethiopia-panel_DATA-CHECK"
author: "Jesse Poland"
date: "3/7/2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(vioplot)
options(max.print=10000)
library(corrplot)

```



The file Et_diversity_panel_metric_traits.txt reports phenotypes for the diversity panel. Data were collected in two locations over two subsequent years, with entries replicated in each field. 

The file contains the following traits:

DB, days to 50% booting (days)
DF, days to 50% flowering (days)
DM, days to full maturity (days)
SPS, number of seeds per spike (n)
SPL, spike length (cm)
PH, plant height (cm)
NET, number of effective tillers (n)
TGW, thousands grain weight (g)
BM, biomass yield (t/ha)
GY, grain yield (t/ha)

```{r}
metric = read.delim(file="/Users/jpoland/Documents/ethiopian_farmers/panel_data/Et_diversity_panel_metric_traits.V2.txt",header=TRUE)
metric[metric=='?']=NA # notes on data cleanup from original: removed blanks -> NA, removed '?'

head(metric)


```





## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
